---
title: "Kermit Perceptions Rank Based Test"
author: "Madeline Berger"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Maddie's first message in document 

Hey Mady Burger
^that is rude Nelson Glen 

Wow, touchy subject...

```{r}

library(tidyverse)

kermit <- read_csv("kermit.csv")

```

```{r}

kerm_hist <- ggplot(kermit, aes(x = Score.pre)) +
  geom_histogram(aes(fill = Gender), bins = 5) +
  facet_wrap(~ Gender)

kerm_hist

```

Maddie: Perform rank-based comparisons using Mann-Whitney U and Wilcoxon -Signed Rank

Question: Is there a significant difference in pre-talk ranks of Kermit for Male and Female respondents? 

```{r}

mwu_kermit <- kermit %>% 
  wilcox.test(Score.pre ~ Gender, data = .)

#Null hypothesis: There is not a significant difference in ranks for male and female respondents

#Alternative: There is a significatn difference in ranks

mwu_kermit

```

"There was no significant difference in ranks for male and female respondents (W = 155.5, p = 0.4, alpha = 0.05)"


Next Quesiton: (Nelson did it)

Is there a significant change in Kermit rankings before nad after his Bren talk?

```{r}

#H0: There is not a significant difference in ranks between pre and post scores

wsr_kermit <- wilcox.test(kermit$Score.pre, kermit$Score.post, paired = TRUE)
wsr_kermit

```

There is no significant difference in ranks for pre- and post-talk Kermit scores (statistical signficance)

